---
title: "Lab 00 - Hello IDS!"
author: "Harry Jackson"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Peter Rabbit", "Amy", "jessica", 
           "adam", "alexander"),
  github_username = c("mcgregors-garden", "amyha11", "jessicapart", 
                      "Adam-Smit05", "AlexanderDug"), 
  colour = c("powderblue", "blue", "green", 
             "green4", "chartreuse"),
  hobby = c("Hopping", "climbing", "rowing", 
            "guitar", "hockey"),
  favourite_number = c(2, 7, 8, 7, 3)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


A bar chart with the usernames as the x axis and favourite numbers as the y axis with the colour of the bars being their respective favourite colours

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Username", 
          y = "Favourite Number",
          title = "My Group")
```



### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

*Remove this text (including the stars) and add your answer for Exercise 20 here.*
